Deciphering Mortality in Alberta: A Multifaceted Analysis

### 2024-03-15 outputs/paper/paper.qmd
paper final draft

---
title: "Modeling Mortality Trends in Alberta"
subtitle: "A Quantitative Approach to Public Health Dynamics"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/Alberta_Mortality_Rate.git"
date: today
date-format: long
abstract: "This study focuses on the mortality trends in Alberta, emphasizing the broader public health implications. It offers a panoramic view of the health challenges and demographic shifts influencing the province's mortality rates. The findings highlight an increase in mortality in recent years, with implications extending beyond individual health conditions to encompass wider societal and environmental factors. This paper underscores the importance of data-driven approaches in shaping effective public health strategies and policies."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Deciphering Mortality in Alberta: A Multifaceted Analysis"
subtitle: "A Quantitative Approach on Demographics, Behaviors, Policies, and Environment"
author: 
  - Ziheng Zhong
thanks: "Code and data are available at: https://github.com/iJustinn/Alberta_Mortality_Rate.git"
date: today
date-format: long
abstract: "This study focuses on the mortality trends in Alberta, emphasizing the broader public health implications. It offers a panoramic view of the health challenges and demographic shifts influencing the province's mortality rates. The findings highlight an increase in mortality in recent years, with implications extending beyond individual health conditions to encompass wider societal and environmental factors. This paper underscores the importance of data-driven approaches in shaping effective public health strategies and policies."
format: pdf
toc: true
toc-depth: 3
number-sections: true
bibliography: references.bib
---
